DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-03 Draft Ped Metrics Example.Rmd
adapt for UGAs and remove cities from UGAs

@@

@@

>>>>

We can also look at regions within the County. For these, we identify the roads and any sidewalks or shoulders.^[In theory, the miles of recorded sidewalk or shoulder and matched miles could be double the centerline miles if every mile had a sidewalk or shoulder.]

@@

```{r plot_ugas}
uga_no_city <- st_as_sf(uga) %>%
  filter(substring(GMA_JURISD, 1, 4) != "City")
kitsap +
  geom_sf(data = uga_no_city, aes(fill = GMA_JURISD), alpha = 0.5) +
  theme_void() +
  labs(title = 'Kitsap County UGAs',
       caption = "Data source: Kitsap GIS - data in development",
       color = "UGAS")

```{r loop_ugas,include=FALSE,echo=FALSE}
the_ugas <- unique(st_set_geometry(uga_no_city, NULL)$GMA_JURISD)
loop_df <- st_as_sf(uga_no_city) %>% mutate(tomatch = GMA_JURISD)

expanded_child <- lapply(
    the_ugas,
    function(x) {
      knitr::knit_expand(file = "child_single_geo.Rmd",
                                   current_geo = x )

Kitsap County has `r length(the_ugas)` UGAs - Urban Growth Areas that are outside of cities. Within the Urban Growth Areas, most design and planning standards are similar to what would be expected in an urban environment for new development.

@@

```
Kitsap County has `r length(the_lamirds)` LAMIRDS - Local Area of More Intense Rural Development.

### 2022-10-03 child_single_geo.Rmd
adapt for UGAs and remove cities from UGAs

```{r} 
library(broom)
this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(road_df, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

# identified a mislabeled RD_LOG_ID in the sidewalk data for Madrone (as Main)
x <- st_as_sf(this_sw_sh) %>% filter(RD_LOG_ID == 49435 & LENGTH > 1000)
x$RD_LOG_ID <- 43809
# x will have 0 rows if we are not dealing with Manchester

@@

          +

@@

Within this area, there are `r this_centerline_miles` centerline road miles; `r this_sw_sh_miles` miles of recorded sidewalk or shoulder (either side of road); and `r this_comb_miles` miles where we could match the recorded sidewalk or shoulder to a road segment (either side of road)^[In theory, the miles of recorded sidewalk or shoulder and matched miles could be double the centerline miles if every mile had a sidewalk or shoulder.]

```{r }
road_sum <- this_roads %>%
  mutate(distance = st_length(.)) %>%  
  st_set_geometry(., NULL) %>% 
  group_by(road_class) %>%
  summarise(t_miles = sum(distance)/5280,
            miles = format(round(as.numeric(sum(distance)/5280), 1), 
                           digits = 1, nsmall=1, big.mark=","),
            .groups = "drop")
df <- select(raod_sum, -t_miles)
colnames(df) <- c("Road Class", "Miles")
knitr::kable(df)
```

```{r}
df <- this_comb %>% st_set_geometry(., NULL) %>% 
  group_by(road_class, SIDE_OF_RO, TYPE) %>%
  summarize(miles = sum(distance)/5280,
            .groups = "drop")
knitr::kable(df)
```

```{r }
p1 <- kitsap +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.5, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) +
  geom_sf(data = this_sw_sh, aes(color = as.factor(TYPE)), show.legend = "line") + 
  sw_sh_col +
  theme_void() +
  labs(title = paste("Map for","{{current_geo}}"),
       caption = "Data source: Kitsap GIS - data in development",
       color = "Pedestrian Facilities")

>>>>

```{r} 
#library(broom)

this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(road_df, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

# need to handle the case where this_sw_sh or this_roads has 0 rows
has_roads <- nrow(this_roads) != 0
has_sw_sh <- nrow(this_sw_sh) != 0
has_both <- has_roads & has_sw_sh
# do not evaluate most of this child if does not
```

```{r, eval=!has_both}
cat("This area does not have either known roads or known sidewalks or shoulders")
```

```{r, eval=has_sw_sh & !has_roads}
this_centerline_miles <- 0 # this_centerline_miles is CENTERLINE MILES TOTAL
# this_sw/sh_miles is RIGHT LEFT MILES with SW or SH TOTAL
this_sw_sh_miles <- format(round(as.numeric(sum(st_length(this_sw_sh))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_comb_miles is RIGHT LEFT MILES where we could match SW/SH to a road segment
this_comb_miles <- 0
```
```{r, eval=!has_sw_sh & has_roads}
# this_centerline_miles is CENTERLINE MILES TOTAL
this_centerline_miles <- format(round(as.numeric(sum(st_length(this_roads))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_sw/sh_miles is RIGHT LEFT MILES with SW or SH TOTAL
this_sw_sh_miles <- 0
# this_sw/sh_miles is RIGHT LEFT MILES where we could match SW/SH to a road segment
this_comb_miles <- 0
```

```{r, eval=has_both}
# identified a mislabeled RD_LOG_ID in the sidewalk data for Madrone (as Main)
x <- st_as_sf(this_sw_sh) %>% mutate(LENGTH = as.integer(LENGTH)) %>% filter(RD_LOG_ID == 49435 & LENGTH > 1000)
x$RD_LOG_ID <- 43809
# x will have 0 rows if we are not dealing with Manchester

@@

Within this area, there are `r this_centerline_miles` centerline road miles; `r this_sw_sh_miles` miles of recorded sidewalk or shoulder (either side of road); and `r this_comb_miles` miles where we could match the recorded sidewalk or shoulder to a road segment (either side of road).

```{r, eval=has_both}

road_sum <- this_roads %>%
  mutate(distance = st_length(.)) %>%  
  st_set_geometry(., NULL) %>% 
  group_by(road_class) %>%
  summarise(t_miles = sum(distance)/5280,
            miles = format(round(as.numeric(sum(distance)/5280), 1), 
                           digits = 1, nsmall=1, big.mark=","),
            .groups = "drop")
df <- select(road_sum, -t_miles)
colnames(df) <- c("Road Class", "Miles")
knitr::kable(df)
```

```{r, eval=has_both}
df <- this_comb %>% st_set_geometry(., NULL) %>% 
  group_by(road_class, SIDE_OF_RO, TYPE) %>%
  summarize(s_miles = sum(distance)/5280,
            miles = format(round(as.numeric(sum(distance)/5280), 1), 
                           digits = 1, nsmall=1, big.mark=","),
            .groups = "drop")
knitr::kable(select(df,-s_miles))
```

```{r, eval=has_both}
p1 <- kitsap +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.5, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) +
  geom_sf(data = this_sw_sh, aes(color = as.factor(TYPE)), show.legend = "line") + 
  sw_sh_col +
  theme_void() +
  labs(title = paste("Map for","{{current_geo}}"),
       caption = "Data source: Kitsap GIS - data in development",
       color = "Pedestrian Facilities")

@@
